\begin{thebibliography}{99}
\bibitem{hadiwardoyo2018} A. Hadiwardoyo, S. Patra, C. T. Calafate, J. C. Cano, and P. Manzoni, "An Intelligent Transportation System Application for Smartphones Based on Vehicle Position Advertising and Route Sharing in Vehicular Ad-Hoc Networks," \textit{Journal of Computer Science and Technology}, vol. 33, no. 2, pp. 249--262, Mar. 2018.

\bibitem{pradip2014} P. S. Pradip and D. K. Vaishali, "Analysis of bus tracking system using GPS on smartphones," \textit{IOSR Journal of Computer Engineering}, vol. 16, no. 1, pp. 1--5, 2014.
\bibitem{fleischer2012} P. B. Fleischer, A. Y. Nelson, R. A. Sowah, and A. A. Bremang, "Design and development of GPS/GSM based vehicle tracking and alert system for commercial inter-city buses," in \textit{2012 IEEE International Conference on Computer Science and Automation Engineering}, vol. 2, pp. 104--107, 2012.
\bibitem{singla2015} L. Singla and P. B. Dr, "GPS based bus tracking system," in \textit{IEEE International Conference on Computer, Communication and Control (IC4-2015)}, 2015.
\bibitem{sankarananrayanan2014} S. Sankarananrayanan and P. Hamilton, "Mobile enabled bus tracking and ticketing system," in \textit{2014 2nd International Conference on Information and Communication Technology (ICoICT)}, 2014.
\bibitem{zhao2020} Y. Zhao and X. Liang, "Optimizing Traffic Signal Control in Urban Road Network with Real-Time GPS Data," \textit{Journal of Intelligent Transportation Systems}, vol. 24, no. 3, pp. 301--312, 2020.
\bibitem{trujillo2020} J. F. Trujillo and P. A. Soto, "Traffic signal optimization with GPS data to improve transportation efficiency," \textit{Transportation Research Part C: Emerging Technologies}, vol. 110, pp. 200--213, 2020.
\bibitem{zhang2019} H. Zhang, L. Liu, and X. Liu, "Real-time Bus Dispatching Based on GPS Information," \textit{Journal of Traffic and Transportation Engineering}, vol. 7, no. 4, pp. 292--299, 2019.
\bibitem{anagnostopoulos2020} T. H. Anagnostopoulos, A. P. Galanopoulos, and M. N. Vrahatis, "Predicting Arrival Times of Public Transportation Buses Using GPS and Machine Learning," \textit{Journal of Intelligent Transportation Systems}, vol. 24, no. 2, pp. 120--132, 2020.
\bibitem{lee2021} J. M. Lee, "Improved Traffic Management through Real-Time Data Integration," \textit{Journal of Urban Planning}, vol. 41, no. 6, pp. 834--841, 2021.
\bibitem{wang2020} X. Wang, L. Zhang, and M. Shen, "Optimization of Public Transport Operations Using GPS and AI Technologies," \textit{Transportation Research Part C: Emerging Technologies}, vol. 114, pp. 112--124, 2020.
\bibitem{vieira2020} M. D. P. Vieira, R. L. E. Dias, and A. F. Pereira, "Transportation optimization using GPS and smartphone applications," \textit{Transportation Research Part D: Transport and Environment}, vol. 79, pp. 134--146, 2020.
\bibitem{song2020} Y. Song and J. Liu, "Integrated Bus Operation Optimization Using Real-Time GPS Data," \textit{Transportation Science}, vol. 54, no. 3, pp. 412--425, 2020.
\bibitem{li2020} M. Li, P. Zhu, and X. Wei, "A Real-Time Bus Scheduling System Based on GPS and Cloud Computing," \textit{Journal of Transportation Engineering}, vol. 146, no. 3, pp. 04020029, 2020.
\bibitem{kumar2020} S. Kumar, "Dynamic Management of Public Transport Systems Using GPS Data," \textit{Journal of Transport and Health}, vol. 17, pp. 25--34, 2020.
\bibitem{xie2021} X. Xie, Y. Liu, and Y. Zhang, "Application of GPS Data in the Optimization of Public Transport Systems," \textit{Journal of Transport Geography}, vol. 87, pp. 57--68, 2021.
\bibitem{zhang2021} Y. Zhang, X. Wang, and J. Li, "Big Data-Driven Optimization of Public Transport Systems Using GPS and Traffic Data," \textit{Transportation Research Part C: Emerging Technologies}, vol. 123, pp. 255--267, 2021.
\bibitem{li2021} J. Li, W. Zhang, and L. Zhao, "Development of GPS-Based Traffic Monitoring and Management System," \textit{Journal of Traffic and Transportation Engineering}, vol. 8, no. 1, pp. 56--65, 2021.
\bibitem{wang2021} Z. Wang, J. Wang, and Q. Liu, "Real-Time Bus Fleet Management Using GPS Data," \textit{Transportation Research Part C: Emerging Technologies}, vol. 119, pp. 34--45, 2021.
\bibitem{zhang2020} Y. Zhang, C. Wei, and L. Zhao, "Using GPS Data for Traffic Management: A Review," \textit{Journal of Intelligent Transportation Systems}, vol. 24, no. 4, pp. 412--423, 2020.

\bibitem{ortuzar2011} J. de D. Ortuzar y L. G. Willumsen, \textit{Modelos de Transporte: Planificacion, Diseno y Evaluacion}, 4a ed., McGraw-Hill, 2011.
\bibitem{vuchic2005} V. R. Vuchic, \textit{Urban Transit: Operations, Planning, and Economics}, Wiley, 2005.
\bibitem{cervero1998} R. Cervero, \textit{The Transit Metropolis: A Global Inquiry}, Island Press, 1998.
\bibitem{agarwal1998} R. Agarwal y J. Prasad, "A Conceptual and Operational Definition of Personal Innovativeness in the Domain of Information Technology," \textit{Information Systems Research}, vol. 9, no. 2, pp. 204--215, 1998.
\bibitem{varshney2002} U. Varshney y R. Vetter, "Mobile Commerce: Framework, Applications and Networking Support," \textit{Mobile Networks and Applications}, vol. 7, no. 3, pp. 185--198, 2002.
\bibitem{schiller2004} J. Schiller y A. Voisard, \textit{Location-Based Services}, Morgan Kaufmann, 2004.
\bibitem{gonzalez2004} A. Gonzalez Fletcher, \textit{Sistema de Posicionamiento Global - GPS}, Escuela Colombiana de Ingenieria, 2004.
\bibitem{manzano2000} F. Manzano Agugliaro, \textit{Aplicacion del Sistema de Posicionamiento Global GPS a la Georreferenciacion y Control Geometrico en la Ingenieria}, Editorial Universidad de Almeria, 2000.
\bibitem{aguilar2017} R. K. Aguilar Villalba et al., \textit{Sistemas de Posicionamiento Global}, Universidad Catolica Boliviana "San Pablo", 2017.

\end{thebibliography}
